%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[landscape,twocolumn,margin=2cm]{geometry}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}
\graphicspath{{./}}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\usepackage{tikz} % Draw graph library

%\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Network Virtualization and Data Center Networks} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Assignment 2a: Proposal\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Erik Henriksson, Christoph Burkhalter} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Proposal}

\subsection{Application}


We will use a simple web-server scenario for the benchmarking and the auto-scaling. There are two types of machines: load-balancers and worker machines. The load-balancers get an IP from a predefined pool of Elastic-IP's such that requests from clients can be sent to them. All load-balancers connect to the overlay network and receive the list of worker machines from the coordinator. Incoming request are sent to a worker machine using a load-balancing technique. In this way load-balancers are connected to all machines in the network, whereas worker machines are only connected to the load-balancers.
The worker machines process the request and contain no further application logic, which means they are not members of the overlay network.
The members of the overlay network (the load-balancers) elect a coordinator and perform a re-electing in case the coordinator dies. We will study the case with exactly two load-balancers, but it is of course easy to scale this up.

\tikzset{
  treenode/.style = {align=center, inner sep=0pt, text centered,
    font=\sffamily},
  load_balancer/.style = {circle, text=white, draw=none,fill=blue},
  node/.style = {circle, text=black, draw=black},
}

\begin{figure}[h!]
\begin{center}
\begin{tikzpicture}[node distance=1cm]
  
  \node [load_balancer] (l1) at (1,2) {L1};
  \node [load_balancer] (l2) at (3,2) {L2};
  \node [node] (n1) at (0,0)  {W1};
  \node [node] (n2) at (2,0) {W2};
  \node [node] (n3) at (4,0)  {W3};

  \foreach \from/\to in {l1/l2,l1/n1,l1/n2,l1/n3,l2/n1,l2/n2,l2/n3}
    \draw (\from) -- (\to);

\end{tikzpicture}
\end{center}

\caption{Network with load balancers (L1,L2) and processing nodes (W1,W2,W3)}
\end{figure}

\subsection{Benchmark}

The benchmark contains latency measurements between machines in the Amazon cloud (cloud to cloud), and a latency test of the application from a client outside the Amazon cloud (client to cloud). Additionally, the benchmarking contains machine performance, mainly CPU speed (optional: memory). The benchmark will be initiated by the coordinator and executed on each machine for the performance benchmark. The latency benchmark is performed on the load-balancers; they test the latency on the network to all running machines in the cloud (other load balancers as well as all the worker machines).

\subsection{Auto-scaling}

The coordinator in the load balancer network performs the auto-scaling. If the load on the worker machines is too large, the coordinator will scale-up some machines or start new machines (scale-out). For the scale-out there will be a snapshot with the installed application to improve the start-up time. 
If the workload decreases, the reverse will be done.
In this part we will compare the Amazon load-balancer with our own implementation of a load-balancer, where we detect heavy-loaded machines if the latency increases or from periodically sending ping messages.

\end{document}
